The Name of the Title Is Hope

### 2025-01-14 paper.tex
added additional example request for why FPG for decoupled lookback

>>>>

\john{It would help at this point to explain why decoupled lookback \emph{also} requires an FPG\@. Your example is good for chained-scan, but the reader would say, well, doesn't decoupled-lookback solve the problem of spinning waiting for a previous block? doesn't it put the resident block to work walking backwards and that resident block will, eventually, reduce everything before it and and be able to make progress?}
